### 2016-04-15 Paper_v5.tex
More discussion updates

@@

However, they often require an exorbitant number of function evaluations to approach the optimum.
Additionally, meta-heuristics require optimization of  algorithm parameters before the actual optimization, and also involve costly update operations to generate parameter diversity.
Thus, for expensive objective functions in complex models with high dimension parameter spaces, meta-heuristics can be inefficient.
Particle Swarm Optimization (PSO) is a population based meta heuristic which does not have any complex operations like recombination, mutation or selection that are associated with other population based meta-heuristics like differential evolution or genetic algorithms.
Several particle swarm variants have been proposed to improve the search ability and rate of convergence. These variations involve different neighborhood structures, multi-swarms or adaptive parameters. Multi-swarm PSO with small particle neighborhoods have been shown to better in searching on complex multi-modal solutions \cite{zhao2008dynamic}.

>>>>

%However, they often require a large number of function evaluations to approach the optimum,
%the optimization of algorithm parameters before the actual optimization, and costly operations to generate parameter diversity.
%Thus, for expensive objective functions in high dimensional parameter spaces, meta-heuristic approaches can be inefficient.

@@

DOPS is a combination of particle swarm optimization, which is a global search method, and dynamically dimensioned search, which is a greedy evolutionary technique.
Particle swarm optimization is a population based meta-heuristic which uses collective information shared amongst swarms of computational particles to
search for global extrema. Several particle swarm variants have been proposed to improve the search ability and rate of convergence. These variations involve different neighborhood structures, multi-swarms or adaptive parameters. Multi-swarm PSO with small particle neighborhoods have been shown to better in searching on complex multi-modal solutions \cite{zhao2008dynamic}.
